Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-16 paper.tex
added citation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, internet of things, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, signal-processing pipelines, and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. Additionally, interaction with real-world entities and addition of modern communication capabilities further enhance the mentioned features and give rise to a new class of systems: embedded \& cyber-physical systems (ECPSs). As a consequence, reliability of ECPSs becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for ECPSs generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct system behavior together with physical plants, providing compliance with target systems, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs. The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding ECPSs. Reliability issues, in the development of ECPSs, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

The interaction between embedded software and physical processes created a different class of systems, which are complex, highly integrated, and present a mixture of continuous and discrete dynamics, named as \textit{hybrid systems} (HSs). Indeed, the embedded-system domain allied to the most recent communication revolution caused an intense integration between different and spread physical processes, which are called embedded \& cyber-physical systems (ECPSs). In particular, the presence of modern communication technologies ({\it e.g.}, internet of things - IoT) causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found in the embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging ECPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute an ECPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, internet of things, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, signal-processing pipelines, and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. Additionally, interaction with real-world entities and addition of modern communication capabilities further enhance the mentioned features and give rise to a new class of systems: embedded \& cyber-physical systems (ECPSs). As a consequence, reliability of ECPSs becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for ECPSs generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct system behavior together with physical plants, providing compliance with target systems, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs. The present survey discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding ECPSs. Reliability issues, in the development of ECPSs, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

The interaction between embedded software and physical processes created a different class of systems, which are complex, highly integrated, and present a mixture of continuous and discrete dynamics, named as \textit{hybrid systems} (HSs). Indeed, the embedded-system domain allied to the most recent communication revolution caused an intense integration between different and spread physical processes, which are called embedded \& cyber-physical systems (ECPSs)~\cite{leeCPS}. In particular, the presence of modern communication technologies ({\it e.g.}, internet of things - IoT) causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found in the embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging ECPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute an ECPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.
